Graph Generators: State of the Art and Open Challenges

### 2019-07-23 comparison.tex
Added stochastic block models
merged 3.5 with 3.1; Tables I and II updated
Consolidation of sectioms 1-2 with the rest

The graph data generators can be classified according to various criteria. For example,~\cite{DBLP:conf/sdm/ChakrabartiZF04} introduces two categories -- degree-based and procedural generators. In general, \emph{degree-based generators} (e.g., Barabasi-Albert model~\cite{Barabasi99emergenceScaling}) are commonly attempting to find a graph that matches it, but without providing any information about the graph or attempting to match other graph features (e.g., eigenvalues, small diameter, ..., etc). On the other hand, \emph{procedural generators} (e.g., R-MAT~\cite{DBLP:conf/sdm/ChakrabartiZF04}) are commonly targeting simple techniques to produce graphs that are matching the characteristics of the real graphs (e.g., the power law degree distribution).

@@

At first we classify the generators on the basis of the respective application domains or user communities. In particular we distinguish (1) general graphs, (2) Semantic Web, (3) graph databases, (4) social networks, (5) graph analytics, (6) community detection, and (7) graph data streaming. The selected classes are not rigorously defined (e.g., they are not disjoint as we will show later), but they correspond to the currently most active research areas. Thus we believe that they form a natural first acquaintance for the reader.

In Table~\ref{tab:comparisonCharacteristics}   we overview the key characteristics of the data generators clustered according to the respective application domains.\footnote{``GDBs'' stands for graph databases, ``SNs'' stands for social networks, ``A'' stands for graph analytics, ``Co'' stands for community detection, and ``St'' stands for graph streaming. Value ``$-$'' means that the information is not available or relevant.} In particular, we show:

\begin{itemize}
\item Characteristics of the \textbf{domain} -- its \textit{type} (column ``Type''), i.e.,  fixed, specified using a schema, or extracted from input data and the particular \textit{target} domain, or, in case of a generic tool, the chosen sample domain (column ``Target/sample''),
\item Characteristics of \textit{read}/\textit{update} \textbf{operations} (columns ``Read'' and ``Update''), i.e., whether the set of operations is fixed/generated, if it involves operation mixes (i.e., sets/sequences of operations), or if templates of operations are supported.
\item Key \textbf{configuration} options:
  \begin{itemize}
    \item whether the generator deals only with structure, or also with \emph{properties} (column ``Pro.'') of the graph (Y/N feature),
    \item supported types of \emph{distributions} (column ``Distributions'') used for generating of the data,
    \item \textit{output format} (column ``Output'') of the produced graph, and
    \item  whether the generator is \textit{distributed} (column ``Dis.'') and thus enables more efficient data generation (Y/N feature).
  \end{itemize}
\end{itemize}

@@

\multirow{5}{*}{\rot{\textbf{General}}}

@@

\multirow{19}{*}{\rot{\textbf{Semantic web}}}

@@

 & LBBM & extracted & Lehigh university BibTeX  & N & N & Y & Monte Carlo &  RDF & N   \\
 & UOBM & fixed & university  & fixed & N & Y & random &  RDF & N   \\

@@

\multirow{7}{*}{\rot{\textbf{SNs}}}

@@

\hline   % ======================   graph analytics
\multirow{1}{*}{\rot{\textbf{A}}}

@@

\multirow{3}{*}{\rot{\textbf{Co}}}
  & Danon et al. & -- & -- & Y & N & N & uniform & edge-list &  N    \\

@@

@@

\hline   %  ======================  streaming
\multirow{2}{*}{\rot{\textbf{St}}}

@@

\paragraph{Number of Generators, Size and Output Format of the Data}
As we can see, the biggest set of available generators can be found in the Semantic Web application domain, probably due to its recent popularity and a number of research groups dealing with this topic. None of these generators is natively implemented in a distributed manner and thus primarily generating  output at the Big Data scale. On the other hand, the \emph{Linked Open Data} (LOD) is expected to be large in general, however this is the case of the whole \emph{LOD Cloud}\footnote{\url{https://lod-cloud.net/}}, but not necessarily of the particular data sets forming it.

@@

\begin{table}
\scriptsize
\centering
\tbl{Overlapping of classes of generators} {
\begin{tabular}{| c | l | l | l | l | l | l | l | l | }
 \hline
           &  \textbf{Generator}
               & \textbf{\rot{General}}
               & \textbf{\rot{Semantic Web}}
               & \textbf{\rot{Graph databases\ }}
               & \textbf{\rot{Social networks}}
               & \textbf{\rot{Analytics}}
               & \textbf{\rot{Community detection}}
               & \textbf{\rot{Streaming}}
               \\ \hline
\hline   % ====================== general graphs
\multirow{5}{*}{\rot{\textbf{General}}}
  & Preferential attachment & {\bf x} & & & & x & & \\
\cline{2-9}
   & R-MAT    & {\bf x} & & & & x & & \\
\cline{2-9}
  & GraphGen  & {\bf x} & & x & & & & \\
\cline{2-9}
%  & Graph 500 & {\bf x} & & & & x & & \\
%\cline{2-9}
  & BTER      & {\bf x} & & & & & & \\
\cline{2-9}
  & Darwini   & {\bf x} & & & & & & \\
\hline
\hline %  ======================  Semantic web
\multirow{15}{*}{\rot{\textbf{Semantic web}}}
 & LUBM  & & {\bf x} & & & & & \\
\cline{2-9}
 & LBBM  & & {\bf x} & & & & & \\
\cline{2-9}
 & UOBM  & & {\bf x} & & & & & \\
\cline{2-9}
 & IIMB & & {\bf x} & & & & & \\
\cline{2-9}
 & BSBM & & {\bf x} & & & & & \\
\cline{2-9}
 & SP$^2$Bench & & {\bf x} & & & & & \\
\cline{2-9}
 & \cite{Duan:2011:AOC:1989323.1989340} & & {\bf x} & & & & & \\
\cline{2-9}
 & DBPSB & & {\bf x} & & & & & \\
\cline{2-9}
 & LODIB & & {\bf x} & & & & & \\
\cline{2-9}
 & SIB & & {\bf x} & & & & & \\
\cline{2-9}
 & Geographica & & {\bf x} & & & & & \\
\cline{2-9}
 & WatDiv & & {\bf x} & & & & & \\
\cline{2-9}
 & RBench & & {\bf x} & & & & & \\
\cline{2-9}
 & LDBC SPB & & {\bf x} & & & & & \\
\cline{2-9}
 & LinkGen & & {\bf x} & & & & & \\
\hline
\hline  % ======================  graph databases
\multirow{3}{*}{\rot{\textbf{GDBs}}}
  & XGDBench & & & {\bf x} & x & & & \\
\cline{2-9}
  & gMark & & x & {\bf x} & x & & & \\
\cline{2-9}
  & graphGen & & & {\bf x} & & & & \\
\hline
\hline %  ======================   social networks
\multirow{7}{*}{\rot{\textbf{SNs}}}
 & \cite{Barrett:2009:GAL:1995456.1995598} & & & & {\bf x} & & & \\
\cline{2-9}
 & \cite{Yao2011}  & & & & {\bf x} & & & \\
\cline{2-9}
 & LinkBench  & & & x & {\bf x} & & & \\
\cline{2-9}
 & S3G2  & & x & x & {\bf x} & & & \\
\cline{2-9}
 & \cite{Sukthankar-SocialInfo2014}  & & & & {\bf x} & & & \\
\cline{2-9}
 & LDBC SNB   & & x & x & {\bf x} & & & \\
\cline{2-9}
  & \cite{Nettleton2016}  & & & & {\bf x} & & & \\
\hline
\hline   % ======================   graph analytics
\multirow{1}{*}{\rot{\textbf{A}}}
  & HPC Scal. Graph Anal.  & & & & & {\bf x} & & \\
%\cline{2-9}
%  & Graphalytics & & & & & {\bf x} & & \\
\hline
\hline   %  ======================  community detection
\multirow{3}{*}{\rot{\textbf{Co}}}
  & Danon et al. & x & & & & x & {\bf x} &\\
\cline{2-9}
  & LFR & x & & & & x & {\bf x} & \\
\cline{2-9}
  & LFR-Overlapping & x & & & & x & {\bf x} & \\
%\cline{2-9}
%  & & & & & & \\
\hline
\hline   %  ======================  streaming
\multirow{2}{*}{\rot{\textbf{St}}}
  & S2Gen & & & & & & & {\bf x}\\
\cline{2-9}
  & RSPLab & & & & & & & {\bf x} \\
%\cline{2-9}
%  & & & & & & & \\
\hline
\end{tabular} }
\label{tab:overlapping}
\end{table}

@@

Similarly, some social network graph generators such as LDBC-SNB, S3G2 or
LinkBench, can be used to test graph databases. In the case of the first two,
even though they are designed not to be specific to any type of technology,
the graph databases are their main target.  Additionally, they also provide serializers for
RDF, thus they can also be used to test RDF systems.

In the case of LinkBench, nothing prevents the user to load the generated graph
in a (graph) database (e.g., Facebook uses MySQL in~\cite{Armstrong:2013:LDB:2463676.2465296}) to
test a workload similar to Facebook and extend and complement it with more
graph queries like those in LDBC-SNB.

>>>>

The graph data generators can be classified according to various criteria. For example,~\cite{DBLP:conf/sdm/ChakrabartiZF04} introduces two categories -- degree-based and procedural generators. In general, \emph{degree-based generators} (e.g., Barabasi-Albert model~\cite{Barabasi99emergenceScaling}) are commonly attempting to find a graph that matches it, but without providing any information about the graph or attempting to match other graph features (e.g., eigenvalues, small diameter, etc). On the other hand, \emph{procedural generators} (e.g., R-MAT~\cite{DBLP:conf/sdm/ChakrabartiZF04}) are commonly targeting simple techniques to produce graphs that are matching the characteristics of the real-world graphs (e.g., the power law degree distribution).

@@

At first we classify the generators on the basis of the respective application domains or user communities. In particular we distinguish (1) general graphs, (2) Semantic Web, (3) graph databases, (4) social networks, and (5) community detection. The selected classes are not rigorously defined (e.g., they are not disjoint as we will show later), but they correspond to the currently most active research areas. Thus we believe that they form a natural first acquaintance for the reader.

In Table~\ref{tab:comparisonCharacteristics}   we overview the key characteristics of the data generators clustered according to the respective application domains.\footnote{``GDBs'' stands for graph databases, ``SNs'' stands for social networks, and ``Co'' stands for community detection. Value ``$-$'' means that the information is not available or relevant.} In particular, we show:

\begin{itemize}
\item Characteristics of the \textbf{domain}:
    \begin{itemize}
      \item its \textit{type} (column ``Type''), i.e.,  fixed, specified using a schema, or extracted from input data, and
      \item the particular \textit{target} domain, or, in case of a generic tool, the chosen sample domain (column ``Target/sample'').
\end{itemize}
\item Characteristics of \textit{read}/\textit{update} \textbf{operations} (columns ``Read'' and ``Update''), i.e., whether the set of operations is fixed/generated, if it involves operation mixes (i.e., sets/sequences of operations), or if templates of operations are supported.
\item Key \textbf{configuration} options:
  \begin{itemize}
    \item whether the generator deals only with structure, or also with \emph{properties} (column ``Pro.'') of the graph (Y/N feature),
    \item supported types of \emph{distributions} (column ``Distributions'') used for generating of the data,
    \item \textit{output format} (column ``Output'') of the produced graph, and
    \item  whether the generator is \textit{distributed} (column ``Dis.'') and thus enables more efficient data generation (Y/N feature).
  \end{itemize}
\end{itemize}

@@

\multirow{6}{*}{\rot{\textbf{General}}}

@@

\multirow{16}{*}{\rot{\textbf{Semantic Web}}}

@@

% & LBBM & extracted & Lehigh university BibTeX  & N & N & Y & Monte Carlo &  RDF & N   \\
% & UOBM & fixed & university  & fixed & N & Y & random &  RDF & N   \\

@@

\multirow{8}{*}{\rot{\textbf{SNs}}}

@@

%\hline
%\hline   % ======================   graph analytics
%\multirow{1}{*}{\rot{\textbf{A}}}
%  & HPC Scal. Graph Anal. & fixed & -- & fixed & N& N& uniform &edge-list & N   \\

@@

\multirow{4}{*}{\rot{\textbf{Co}}}
  & \cite{danon2005comparing} & -- & -- & Y & N & N & uniform & edge-list &  N    \\

@@

  & Stochastic Block Models & -- & -- & Y & N & N & user-defined & edge-list & Y     \\

@@

%\hline   %  ======================  streaming
%\multirow{2}{*}{\rot{\textbf{St}}}
%  & S2Gen & schema-driven & social network & Y & N & N & user-defined & RDF & N     \\
%  & RSPLab & schema-driven & agnostic & Y & Y & N & user-defined & RDF & N     \\

@@

\paragraph{Number of Generators, Size and Output Format of the Data}
As we can see, the biggest set of available generators can be found in the Semantic Web application domain, probably due to its recent popularity and a number of research groups dealing with this topic. None of these generators is natively implemented in a distributed manner and thus primarily generating  output at the Big Data scale. On the other hand, the \emph{Linked Open Data} (LOD) is expected to be large in general; however, this is the case of the whole \emph{LOD Cloud}\footnote{\url{https://lod-cloud.net/}}, but not necessarily of the particular data sets forming it.

@@

\begin{table}
\scriptsize
\centering
\tbl{Overlapping of classes of generators} {
\begin{tabular}{| c | l | l | l | l | l | l | l | }
 \hline
           &  \textbf{Generator}
               & \textbf{\rot{General}}
               & \textbf{\rot{Semantic Web}}
               & \textbf{\rot{Graph databases\ }}
               & \textbf{\rot{Social networks}}
               %& \textbf{\rot{Analytics}}
               & \textbf{\rot{Community detection\ }}
               %& \textbf{\rot{Streaming}}
               \\ \hline
\hline   % ====================== general graphs
\multirow{6}{*}{\rot{\textbf{General}}}
  & Preferential attachment & {\bf x} & & &  & \\
\cline{2-7}
   & R-MAT    & {\bf x} & & &  &  \\
\cline{2-7}
   & HPC Scal. Graph Anal.  & {\bf x} & & &  &  \\
\cline{2-7}
  & GraphGen  & {\bf x} & & x &  & \\
\cline{2-7}
%  & Graph 500 & {\bf x} & & &  & \\
%\cline{2-7}
  & BTER      & {\bf x} & & &  & \\
\cline{2-7}
  & Darwini   & {\bf x} & & &  & \\
\hline
\hline %  ======================  Semantic web
\multirow{14}{*}{\rot{\textbf{Semantic web}}}
 & LUBM  & & {\bf x} & &  &  \\
\cline{2-7}
% & LBBM  & & {\bf x} & &  &  \\
%\cline{2-7}
% & UOBM  & & {\bf x} & &  &  \\
%\cline{2-7}
 & IIMB & & {\bf x} & &  & \\
\cline{2-7}
 & BSBM & & {\bf x} & &  &  \\
\cline{2-7}
 & SP$^2$Bench & & {\bf x} & &  &  \\
\cline{2-7}
 & \cite{Duan:2011:AOC:1989323.1989340} & & {\bf x} & &  &  \\
\cline{2-7}
 & DBPSB & & {\bf x} & &  &  \\
\cline{2-7}
 & LODIB & & {\bf x} & &  &  \\
\cline{2-7}
% & SIB & & {\bf x} & &  &  \\
%\cline{2-7}
 & Geographica & & {\bf x} & &  &  \\
\cline{2-7}
 & WatDiv & & {\bf x} & &  &  \\
\cline{2-7}
 & RBench & & {\bf x} & &  &  \\
\cline{2-7}
  & S2Gen & & {\bf x} & &  &  \\
\cline{2-7}
  & RSPLab & & {\bf x} & &  &  \\
\cline{2-7}
 & LDBC SPB & & {\bf x} & &  &  \\
\cline{2-7}
 & LinkGen & & {\bf x} & &  &  \\
\hline
\hline  % ======================  graph databases
\multirow{3}{*}{\rot{\textbf{GDBs}}}
  & XGDBench & & & {\bf x} & x  &  \\
\cline{2-7}
  & gMark & & x & {\bf x} & x  &  \\
\cline{2-7}
  & graphGen & & & {\bf x} &  &  \\
\hline
\hline %  ======================   social networks
\multirow{8}{*}{\rot{\textbf{SNs}}}
 & \cite{Barrett:2009:GAL:1995456.1995598} & & & & {\bf x}  & \\
\cline{2-7}
 & \cite{Yao2011}  & & & & {\bf x}  & \\
\cline{2-7}
 & LinkBench  & & & x & {\bf x}  & \\
\cline{2-7}
 & S3G2  & & x & x & {\bf x}  & \\
\cline{2-7}
 & SIB & & x & & {\bf x}  &  \\
\cline{2-7}
 & \cite{Sukthankar-SocialInfo2014}  & & & & {\bf x}  & \\
\cline{2-7}
 & LDBC SNB   & & x & x & {\bf x}  & \\
\cline{2-7}
  & \cite{Nettleton2016}  & & & & {\bf x}  &  \\
%\hline
%\hline   % ======================   graph analytics
%\multirow{1}{*}{\rot{\textbf{A}}}
%  & HPC Scal. Graph Anal.  & & & & &  \\
%\cline{2-7}
%  & Graphalytics & & & & &  \\
\hline
\hline   %  ======================  community detection
\multirow{4}{*}{\rot{\textbf{Co}}}
  & \cite{danon2005comparing} & x & & & &  {\bf x} \\
\cline{2-7}
  & LFR & x & & & &  {\bf x}  \\
\cline{2-7}
  & LFR-Overlapping & x & & & &  {\bf x} \\
\cline{2-7}
  & Stochastic Block Models & x & & & &  {\bf x} \\
%\cline{2-7}
%  & & & & &  \\
\hline
%\hline   %  ======================  streaming
%\multirow{2}{*}{\rot{\textbf{St}}}
%  & S2Gen & & & & & & & {\bf x}\\
%\cline{2-7}
%  & RSPLab & & & & & & & {\bf x} \\
%%\cline{2-7}
%%  & & & & & & \\
%\hline
\end{tabular} }
\label{tab:overlapping}
\end{table}

@@

Similarly, some social network graph generators such as LDBC SNB, S3G2 or
LinkBench, can be used to test graph databases. In the case of the first two,
even though they are designed not to be specific to any type of technology,
the graph databases are their main target.  Additionally, they also provide serializers for
RDF, thus they can also be used to test RDF systems.

In the case of LinkBench, nothing prevents the user to load the generated graph
in a (graph) database (e.g., Facebook uses MySQL in~\cite{Armstrong:2013:LDB:2463676.2465296}) to
test a workload similar to Facebook and extend and complement it with more
graph queries like those in LDBC SNB.

### 2019-07-23 introduction.tex
Minor changes
Removed section 4, modified bibliography
Consolidation of sectioms 1-2 with the rest

In general, we can distinguish between two broad types of graph data sets: (1) a single large graph (possibly with several components), such as social networks  or Linked Data graphs, and (2) a large set of small graphs, such as chemical compounds\footnote{\url{https://pubchem.ncbi.nlm.nih.gov/}} or linguistics syntax trees\footnote{\url{https://catalog.ldc.upenn.edu/ldc99t42}}. Naturally, the algorithms used in theses two classes differ a lot~\cite{DBLP:books/igi/Sakr2011}. In the former case we can search, e.g., for communities and their features or shortest paths, while in the latter case we usually query for supergraphs, subgraphs or graphs similar to a given graph pattern. In both the cases, as in the other fields, quite often the respective real-world graph data is not publicly available (or simply does not exist when a particular method for data manipulation is proposed).
Even in the cases in which real data is abundant, many algorithms and techniques need to be tested on various order of magnitudes of the graph sizes thus leading to the inception of
configurable graph generators that reproduce real-world graph properties and provide unique tuning opportunities for
algorithms and tools handling such data.
%As a consequence, also in the world of graphs there has appeared a number of graph data generators which enable to  reproduce the respective real-world linking properties and gauge the effectiveness of a particular algorithm.

In this survey, we provide a comprehensive overview of the state-of-the-art
modern
graph generators by focusing on those that are pertinent and suitable for
data-intensive tasks. Our aim is to cover a wide range of currently popular
areas of graph data processing. In particular, we consider graph generation
in the areas of graph databases, Semantic Web, social networks, graph streaming, alongside community detection  and graph data analytics. Despite the disparate requirements of modern graph generators throughout these communities, we analyze them under a common umbrella, reaching out the functionalities, the practical usage, and the supported operations of graph generators. The reasons for this scope and classification are as follows:

\begin{enumerate}
  \item Despite the differences of the covered areas, the requirements for
modern graph data generators can be similar in particular cases. Reusing or learning from tools in other fields can thus bring new opportunities for both researchers and practitioners.
  \item The selected classification is serving the need of providing scientists, researchers and practitioners with the right data generator at hand for their work.
\end{enumerate}

@@

\paragraph*{Contributions} Our survey revisits the representatives of
modern graph data generators and summarizes their major features. The comprehensive review and analysis make this paper useful for motivating new graph data generation techniques as well as serving as a technical reference for selecting suitable solutions. In particular, the introductory categorization and comparative study enables the reader to quickly get his/her bearings in the field and identify a subset of generators of his/her interest. Since we do not limit the survey to a particular area of graph data management,  the reader can get a broader scope in the field. Hence, while practitioners can find a solution in another previously unexpected area, researchers can identify new target areas or exploit successful results in new fields. Last but not least, to provide a global view of the state-of-the-art, we also provide an overview of most commonly used real-world testing graph datasets. And, finally, we identify general open problems of graph data synthesis and indicate possible solutions to show that it still forms a challenging and promising research area.

@@

To the best of our knowledge, our work is the first to survey the broad
landscape of graph data generators spanning different data-intensive applications and
targeting many computer science subfields. In particular, we cover graph databases, Semantic Web, social networks, graph streaming, community detection, and graph data analytics. However, the literature is still lacking a comprehensive study of graph generators  for many of the specific subfields mentioned above.

A limited subset of graph database
generators, parallel and distributed graph processing generators, along
with a few of the Semantic Web data generators presented in our survey have
been discussed in a related book chapter
\cite{BFHI18} while cross-comparing them with respect to input, output,
supported workload, data model and query language, along with the
distinguished chokepoints. However, the provided classification is
inherently database-oriented.
In our work, we provide a more comprehensive and broader classification
 that serves the purpose of letting any
researcher or practitioner interested in data generation  to be able to make a better
choice of the desired graph
generator based on its functional and goal-driven features (such as the application domain,
the supported operations and the key configuration options).
Moreover, in contrast with \cite{BFHI18}, our work encompasses graph generators of several
diverse communities, not limiting its scope to a few generators of the database
and graph processing communities.

Graph generators matching graph patterns used in data mining have been
studied in \cite{Chakrabarti:2006:GML:1132952.1132954},
focusing on mostly occurring patterns, such as power laws, size of graph diameters
and community structure. The considered graph generators are compared in
terms of graph type, degree distributions, exponentiality, diameter and
community effects. We refer the reader to this survey for taxonomies
involving these properties, whereas we provide here a functionality-driven
taxonomy across all the categories of graph generators that we consider.
We also point out that this survey is outdated as it does not consider the
generators that appeared in the last decade.
We fill the gap of more recent social network and graph analytics generators
respectively in Section 3.4 and 3.5.

@@

Aggarwal and Subbian~\cite{AggarwalS14} have surveyed the evolution of analysis in
graphs, by primarily focusing on data mining maintenance methods and on analytical
quantification and explanation of the changes of the underlying networks.
A brief discussion on evolutionary
network data generators is carried out in
the paper. The data generation of evolutionary networks is based on
Densification Power Law (DPL) and shrinking diameters, community-guided
attachment properties~\cite{Leskovec:2005:GOT:1081870.1081893}.
Generation of graphs tackling Kronecker
recursion with recursive tensor multiplication~\cite{AkogluMF08} is then considered in the above survey.
We refer the readers to the aforementioned survey for evolutionary network generators and further discuss the open challenges of evolving graph data in Section 5.
%\TODO{Better highlight the differences when Sherif's part is in.}

@@

\paragraph*{Outline} The rest of this paper is organized as follows: Section~\ref{sec:comparison}  provides the opening categorization and comparison of the generators. Section~\ref{sec:generators} provides an overview of the existing graph data generators and their main features in the frame of the proposed categories. To provide a complete overview,  we list the most commonly used testing data sets for the particular categories in Section~\ref{sec:data_sets}.  In Section~\ref{sec:challenges}, we highlight some of the challenges and open problems of graph data synthesis before we conclude in Section~\ref{sec:conclusion}.

>>>>

In general, we can distinguish between two broad types of graph data sets: (1) a single large graph (possibly with several components), such as social networks  or Linked Data graphs, and (2) a large set of small graphs, such as chemical compounds\footnote{\url{https://pubchem.ncbi.nlm.nih.gov/}} or linguistics syntax trees\footnote{\url{https://catalog.ldc.upenn.edu/ldc99t42}}. Naturally, the algorithms used in theses two classes differ a lot~\cite{DBLP:books/igi/Sakr2011}. In the former case we can search, e.g., for communities and their features or shortest paths, while in the latter case we usually query for supergraphs, subgraphs, or graphs similar to a given graph pattern. In both the cases, as in the other fields, quite often the respective real-world graph data is not publicly available (or simply does not exist when a particular method for data manipulation is proposed).
Even in the cases in which real data is abundant, many algorithms and techniques need to be tested on various orders of magnitudes of the graph sizes thus leading to the inception of
configurable graph generators that reproduce real-world graph properties and provide unique tuning opportunities for
algorithms and tools handling such data.
%As a consequence, also in the world of graphs there has appeared a number of graph data generators which enable to  reproduce the respective real-world linking properties and gauge the effectiveness of a particular algorithm.

In this survey, we provide a comprehensive overview of the state-of-the-art
modern
graph generators by focusing on those that are pertinent and suitable for
data-intensive tasks. Our aim is to cover a wide range of currently popular
areas of graph data processing. In particular, we consider graph generation
in the areas of Semantic Web, graph databases, social networks, and community detection, along with general graphs. Despite the disparate requirements of modern graph generators throughout these communities, we analyze them under a common umbrella, reaching out the functionalities, the practical usage, and the supported operations of graph generators. The reasons for this scope and classification are as follows:

\begin{enumerate}
  \item Despite the differences of the covered areas, the requirements for
modern graph data generators can be similar in particular cases. Reusing or learning from tools in other fields can thus bring new opportunities for both researchers and practitioners.
  \item The selected classification is serving the need of providing scientists, researchers, and practitioners with the right data generator at hand for their work.
\end{enumerate}

@@

\paragraph*{Contributions} Our survey revisits the representatives of
modern graph data generators and summarizes their major features. The comprehensive review and analysis make this paper useful for motivating new graph data generation techniques as well as serving as a technical reference for selecting suitable solutions. In particular, the introductory categorization and comparative study enables the reader to quickly get his/her bearings in the field and identify a subset of generators of his/her interest. Since we do not limit the survey to a particular area of graph data management,  the reader can get a broader scope in the field. Hence, while practitioners can find a solution in another previously unexpected area, researchers can identify new target areas or exploit successful results in new fields. Last but not least, %to provide a global view of the state-of-the-art, we also provide an overview of most commonly used real-world testing graph datasets. And, finally,
we identify general open problems of graph data synthesis and indicate possible solutions to show that it still forms a challenging and promising research area.

@@

To the best of our knowledge, our work is the first to survey the broad
landscape of graph data generators spanning different data-intensive applications and
targeting many computer science subfields. In particular, we cover Semantic Web, graph databases, social networks, and community detection, along with general graphs. However, the literature is still lacking a comprehensive study of graph generators  for many of the specific subfields mentioned above.

A limited subset of graph database
generators, parallel and distributed graph processing generators, along
with a few of the Semantic Web data generators presented in our survey have
been discussed in a related book chapter
\cite{BFHI18} while cross-comparing them with respect to input, output,
supported workload, data model and query language, along with the
distinguished chokepoints. However, the provided classification is
inherently database-oriented.
In our work, we provide a more comprehensive and broader classification
 that serves the purpose of letting any
researcher or practitioner interested in data generation  to be able to make a better
choice of the desired graph
generator based on its functional and goal-driven features (such as the application domain,
the supported operations, and the key configuration options).
Moreover, in contrast with \cite{BFHI18}, our work encompasses graph generators of several
diverse communities, not limiting its scope to a few generators of the database
and graph processing communities.

Graph generators matching graph patterns used in data mining have been
studied in \cite{Chakrabarti:2006:GML:1132952.1132954},
focusing on mostly occurring patterns, such as power laws, size of graph diameters,
and community structure. The considered graph generators are compared in
terms of graph type, degree distributions, exponentiality, diameter, and
community effects. We refer the reader to this survey for taxonomies
involving these properties, whereas we provide here a functionality-driven
taxonomy across all the categories of graph generators that we consider.
We also point out that this survey is outdated as it does not consider the
generators that appeared in the last decade.
We fill the gap of more recent social network generators
in Section~\ref{sec:generators_socialnetworks}, as well as more recent representatives of the other categories.

@@

Aggarwal and Subbian~\cite{AggarwalS14} have surveyed the evolution of analysis in
graphs, by primarily focusing on data mining maintenance methods and on analytical
quantification and explanation of the changes of the underlying networks.
A brief discussion on evolutionary
network data generators is carried out in
the paper. The data generation of evolutionary networks is based on the
Densification Power Law (DPL) and shrinking diameters, community-guided
attachment properties~\cite{Leskovec:2005:GOT:1081870.1081893}.
Generation of graphs tackling Kronecker
recursion with recursive tensor multiplication~\cite{AkogluMF08} is then considered in the above survey.
We refer the readers to the aforementioned survey for evolutionary network generators and further 
discuss the open challenges of evolving graph data in Section~\ref{sec:challenges}.
%\TODO{Better highlight the differences when Sherif's part is in.}

@@

\paragraph*{Outline} The rest of this paper is organized as follows: Section~\ref{sec:comparison}  
provides the opening categorization and comparison of the generators. Section~\ref{sec:generators} 
provides an overview of the existing graph data generators and their main features in the frame of 
the proposed categories. 
%To provide a complete overview,  we list the most commonly used testing data sets for the particular categories in Section~\ref{sec:data_sets}.
In Section~\ref{sec:challenges}, we highlight some of the challenges and open problems of graph 
data synthesis before we conclude in Section~\ref{sec:conclusion}.

### 2019-07-23 main.tex
updated year main.tex
Minor changes
Removed section 4, modified bibliography
Consolidation of sectioms 1-2 with the rest

% Metadata Information
\acmVolume{0}
\acmNumber{0}
\acmArticle{0}
\acmYear{2018}
\acmMonth{0}

@@

\begin{abstract}
The abundance of interconnected data has fueled the design and
implementation of graph generators reproducing real-world linking
properties, or gauging the effectiveness of graph algorithms, techniques
and applications manipulating these data. We consider graph generation
across multiple subfields, such as graph databases, Semantic Web, social networks, graph streaming, alongside community detection  and graph data analytics. Despite the disparate
requirements of modern graph generators throughout these communities, we
analyze them under a common umbrella, reaching out the functionalities, the
practical usage, and their supported operations.
We argue that this classification is serving the need of providing scientists, researchers and practitioners with the right data generator at hand for their work.

@@

\acmformat{A. Bonifati, I. Holubov\'{a}, A. Prat-P\'erez, S. Sakr, 2018.
Modern Graph Generators: A Survey.}
% At a minimum you need to supply the author names, year and a title.
% IMPORTANT:
% Full first names whenever they are known, surname last, followed by a period.
% In the case of two authors, 'and' is placed between them.
% In the case of three or more authors, the serial comma is used, that is, all author names
% except the last one but including the penultimate author's name are followed by a comma,
% and then 'and' is placed before the final author's name.
% If only first and middle initials are known, then each initial
% is followed by a period and they are separated by a space.
% The remaining information (journal title, volume, article number, date, etc.) is 'auto-generated'.

@@

\input{introduction}
%\input{preliminaries}
\input{comparison}
%\input{classification}
\input{generators}
%\input{comparison2}
\input{data_sets}
\input{challenges}
\input{conclusion}

@@

% History dates
\received{October 2018}{October 2018}{October 2018}

>>>>

% Metadata Information
\acmVolume{0}
\acmNumber{0}
\acmArticle{0}
\acmYear{2019}
\acmMonth{0}

@@

\begin{abstract}
The abundance of interconnected data has fueled the design and
implementation of graph generators reproducing real-world linking
properties, or gauging the effectiveness of graph algorithms, techniques
and applications manipulating these data. We consider graph generation
across multiple subfields, such as Semantic Web, graph databases, social networks, and community detection, along with general graphs. Despite the disparate
requirements of modern graph generators throughout these communities, we
analyze them under a common umbrella, reaching out the functionalities, the
practical usage, and their supported operations.
We argue that this classification is serving the need of providing scientists, researchers and practitioners with the right data generator at hand for their work.

@@

\acmformat{A. Bonifati, I. Holubov\'{a}, A. Prat-P\'erez, S. Sakr, 2019.
Modern Graph Generators: A Survey.}
% At a minimum you need to supply the author names, year and a title.
% IMPORTANT:
% Full first names whenever they are known, surname last, followed by a period.
% In the case of two authors, 'and' is placed between them.
% In the case of three or more authors, the serial comma is used, that is, all author names
% except the last one but including the penultimate author's name are followed by a comma,
% and then 'and' is placed before the final author's name.
% If only first and middle initials are known, then each initial
% is followed by a period and they are separated by a space.
% The remaining information (journal title, volume, article number, date, etc.) is 'auto-generated'.

@@

\input{introduction}
%\input{preliminaries}
\input{comparison}
%\input{classification}
\input{generators}
%\input{comparison2}
%\input{data_sets}
\input{challenges}
\input{conclusion}

@@

% History dates
\received{June 2019}{June 2019}{June 2019}
